### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
start doing todo.md

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current, which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some pinholes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurements exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-optimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{C}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{C}$.

@@

%
%5F ca 100min
%4F ca 140min
%3F ca 420min (7h)
%extra AcOH stabilzed but needed so much that dilution too large...
%\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
%same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
%of 1:5 is unacceptable Dilution }
%- 21.8 (1F) from 15.02. 13:30 bis 
%26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
%18.02 4F in 80min milky
%      2F in ca 24h (stabilization AcOH)
%
%acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
%\Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
%Multiple question still need to be answered: 
%What causes the cloudiness (as stability increased through sealing probably \ch{H2O} from the air or \ch{O2}) and what's the mechanism? 
%How does \gls{ipo} increase the stability? 
%Does it do so because it "fits" better with the solvent. 
%As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}. 
%It was even observed that the addition of \td{some drops of} \gls{ipo} to an acetic solution can clear the solution.
%5F acetic solution milky over night 5:1 dilution with \gls{ipo} and clear after one minute of stirring and stayed clear over 5 nights.
% more details on pages 68ff
%No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
%\todo{Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
%The stirring time was untersucht, but not much difference so shortest was used because 
%short time can produces faster and the resulting solution is longer stable 
%(after finishing mixing)

@@

%- first recipe tried to improve to achieve more resisting layer. 
%by pH value, surface tension and solution ratios 
%(only 10\% change because it was assumed, that the recipe is good and should be improved, 
%but the recipe should be altered thoroughly. 
%two layers were also tried but didn't even pass the visual examination/test/inspection. 
%A curst was produced. 
%It is assumed

>>>>

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current, which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e.\ the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some pinholes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurements exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-optimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} speed $v_{C}$ (i.e.\ the speed with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} speed, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} speed $v_{C}$.

@@

%
%5F ca 100min
%4F ca 140min
%3F ca 420min (7h)
%extra AcOH stabilzed but needed so much that dilution too large...
%\td{IPO influence on "stability" p74: 600ul IPO makes clear, 4000 ul BuOH not clear with 
%same base solution (1ml of 4F), added extra 400ul to BuOH sol and after 5min clear. 
%of 1:5 is unacceptable Dilution }
%- 21.8 (1F) from 15.02. 13:30 bis 
%26.3 (1ml iPO to ca2ml of 5f) from 16.02. 16:30 bis 18.02.++
%18.02 4F in 80min milky
%      2F in ca 24h (stabilization AcOH)
%
%acceptable layer was produced by buthanolic solution, but very unstable (short lived) how long? p41 
%\Gls{ipo} solution allowed to even reuse high concentrated solution, which would otherwise become cloudy under 60 minutes. 
%Multiple question still need to be answered: 
%What causes the cloudiness (as stability increased through sealing probably \ch{H2O} from the air or \ch{O2}) and what's the mechanism? 
%How does \gls{ipo} increase the stability? 
%Does it do so because it "fits" better with the solvent. 
%As the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}. 
%It was even observed that the addition of \td{some drops of} \gls{ipo} to an acetic solution can clear the solution.
%5F acetic solution milky over night 5:1 dilution with \gls{ipo} and clear after one minute of stirring and stayed clear over 5 nights.
% more details on pages 68ff
%No effect on the solution or the resulting layer was noticed \td{from the initial stirring}
%\todo{Following stirring times (in minutes) were tested and did not have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180.}
%The stirring time was untersucht, but not much difference so shortest was used because 
%short time can produces faster and the resulting solution is longer stable 
%(after finishing mixing)

@@

%- first recipe tried to improve to achieve more resisting layer. 
%by pH value, surface tension and solution ratios 
%(only 10\% change because it was assumed, that the recipe is good and should be improved, 
%but the recipe should be altered thoroughly. 
%two layers were also tried but did not even pass the visual examination/test/inspection. 
%A curst was produced. 
%It is assumed
